---
title: "Association analysis of trending words Black world/ Negro Digest"
author: "Kushal K Dey"
date: "4/16/2018"
output: html_document
---

## Introduction

In this script, we look at some interesting words that show a contrary to 
expected trends in their association with identity terms *black* and *negro*.

```{r}
library(wordVectors)
library(ggplot2)
```

## Load word2vec models

We load the word2vec model fits.

### Null identity models

```{r warning = FALSE, message=FALSE}
dir <- "../BL_ND_ID/"
ll <- list.files(dir, pattern = ".bin")
model_list_1 <- list()
for(m in 1:length(ll)){
  model_list_1[[m]] = read.vectors(paste0(dir, ll[m]))
}
```


### Full model

```{r warning = FALSE, message=FALSE}
dirs <- c("../Negro_Digest/ND_1961/",
          "../Negro_Digest/ND_1962/",
          "../Negro_Digest/ND_1963/",
          "../Negro_Digest/ND_1964/",
          "../Negro_Digest/ND_1965/",
          "../Negro_Digest/ND_1966/",
          "../Negro_Digest/ND_1967/",
          "../Negro_Digest/ND_1968/",
          "../Negro_Digest/ND_1969/",
          "../Negro_Digest/ND_1970/",
          "../Black_World/BL_1970/",
          "../Black_World/BL_1971/",
          "../Black_World/BL_1972/",
          "../Black_World/BL_1973/",
          "../Black_World/BL_1974/",
          "../Black_World/BL_1975/",
          "../Black_World/BL_1976/")


model_list_2 <- list()
for(m in 1:length(dirs)){
  model_list_2[[m]] = read.vectors(paste0(dirs[m], "pooled_word2vec.bin"))
}
```

## Association Trend Plotter 

```{r}
trend_plotter <- function(word_set_1, word_set_2, model_list){
  assoc <- c()
  for(m in 1:length(ll)){
  
  assoc <- c(assoc, 
             cosineSimilarity(model_list[[m]][[word_set_1, average = TRUE]], 
                              model_list[[m]][[word_set_2, average = TRUE]]))
  }
  df <- data.frame("year" =  c(1961:1970, 1970:1976),
                   "score" = assoc)
  p <- qplot(year, score, data = df, xlab = "year", ylab = "association score") +  
            geom_smooth(method = "lm", size = 1.5) +
            ggtitle("trend plot")
  p
}
```


## [Black, Negro] vs struggle

```{r}
trend_plotter(c("black", "blacks"), c("struggle"), model_list_1)
```

## [Black] vs struggle

```{r}
trend_plotter(c("black", "blacks"), c("struggle"), model_list_2)
```


## [Negro] vs struggle

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("struggle"), model_list_2)
```

## [Black, Negro] vs leadership

```{r}
trend_plotter(c("black", "blacks"), c("leadership"), model_list_1)
```

## [Black] vs leadership

```{r}
trend_plotter(c("black", "blacks"), c("leadership"), model_list_2)
```

## [Negro] vs leadership

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("leadership"), model_list_2)
```

## [Black, Negro] vs leadership

```{r}
trend_plotter(c("black", "blacks"), c("independence"), model_list_1)
```

## [Black] vs leadership

```{r}
trend_plotter(c("black", "blacks"), c("independence"), model_list_2)
```

## [Negro] vs leadership

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("independence"), model_list_2)
```

## [Black, Negro] vs father

```{r}
trend_plotter(c("black", "blacks"), c("father"), model_list_1)
```

## [Black] vs leadership

```{r}
trend_plotter(c("black", "blacks"), c("father"), model_list_2)
```

## [Negro] vs leadership

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("father"), model_list_2)
```

## [Black, Negro] vs community

```{r}
trend_plotter(c("black", "blacks"), c("community"), model_list_1)
```

## [Black] vs community

```{r}
trend_plotter(c("black", "blacks"), c("community"), model_list_2)
```


## [Negro] vs community

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("community"), model_list_2)
```

## [Black, Negro] vs vote

```{r}
trend_plotter(c("black", "blacks"), c("vote", "voters"), model_list_1)
```

## [Black] vs vote

```{r}
trend_plotter(c("black", "blacks"), c("vote", "voters"), model_list_2)
```

## [negro] vs vote

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("vote", "voter", "voters"), model_list_2)
```

## [Black] vs father

```{r}
trend_plotter(c("black"), c("father", "mother"), model_list_2)
```

## [negro] vs father

```{r}
trend_plotter(c("negro"), c("mother", "father"), model_list_2)
```

