---
title: 'Negro Digest/Black World : 1961-1975, text processing'
author: "Kushal K Dey"
date: "4/11/2018"
output: html_document
---

```{r include=TRUE, eval=TRUE, warning=FALSE, message = FALSE}
library(wordVectors)
```

## Introduction

In this script, we process the text data from Negro Digest/ Black World magazine from 1961-1975 (Negro Digest 
changed its name to Black World in 1970) and then fit the word2vec model, and save the word2vec results - to be 
used subsequently by other scripts. In the process, we also create a table of counts of occurrences of each word in Ebony in each year of the magazine's publication.

```{r message=FALSE, warning=FALSE}
dirs <- c("../Negro_Digest/ND_1961/",
          "../Negro_Digest/ND_1962/",
          "../Negro_Digest/ND_1963/",
          "../Negro_Digest/ND_1964/",
          "../Negro_Digest/ND_1965/",
          "../Negro_Digest/ND_1966/",
          "../Negro_Digest/ND_1967/",
          "../Negro_Digest/ND_1968/",
          "../Negro_Digest/ND_1969/",
          "../Negro_Digest/ND_1970/",
          "../Black_World/BL_1970/",
          "../Black_World/BL_1971/",
          "../Black_World/BL_1972/",
          "../Black_World/BL_1973/",
          "../Black_World/BL_1974/",
          "../Black_World/BL_1975/",
          "../Black_World/BL_1976/")
```


## Processing texts 

Combining the issues from each year into a pooled text file.

```{r message=FALSE, warning=FALSE}
for(m in 1:length(dirs)){
  out <- prep_word2vec(origin = dirs[m], destination = paste0(dirs[m],"pooled.txt"), lowercase = T)
}
```

## Words used in Ebony

Making a list of words used by Ebony articles across the 16 years 1961-1976.

```{r message = FALSE, warning=FALSE}
all_names <- c()
for(m in 1:length(dirs)){
  sentences<-scan(paste0(dirs[m], "pooled.txt"),"character",sep="\n");
  #Replace full stop and comma
  sentences<-gsub("\\.","",sentences)
  sentences<-gsub("\\,","",sentences)
  #Split sentence
  words<-strsplit(sentences," ")
  #Calculate word frequencies
  words.freq<-table(unlist(words));
  all_names <- union(all_names , names(words.freq))
}
```

## Frequencies of the words

Tabulating the counts of the occurrences of these words every year.

```{r}
tab <- matrix(0, length(dirs), length(all_names))
colnames(tab) <- all_names
rownames(tab) <- c(paste0("ND_", 1961:1970), paste0("BL_", 1970:1976))

for(m in 1:length(dirs)){
  sentences<-scan(paste0(dirs[m], "pooled.txt"),"character",sep="\n");
  #Replace full stop and comma
  sentences<-gsub("\\.","",sentences)
  sentences<-gsub("\\,","",sentences)
  #Split sentence
  words<-strsplit(sentences," ")
  #Calculate word frequencies
  words.freq<-table(unlist(words));
  tab[m, match(names(words.freq), colnames(tab))] <- as.numeric(words.freq)
}

```

We take a sneak peek at the table of counts 

```{r}
tab[1:5,1:5]
```

We save both the list of words in Ebony and also the table of their counts of occurrence per year.

```{r}
save(all_names, file = "../output/all_words_BL_ND.rda")
save(tab, file = "../output/table_word_frequencies_BL_ND.rda")
```

## SessionInfo

```{r}
sessionInfo()
```

