---
title: 'Consistent word pairs trends : Ebony'
author: "Kushal K Dey"
date: "4/20/2018"
output: html_document
---

## Introduction

In this script, we look at some interesting words that show a contrary to 
expected trends in their association with identity terms *black* and *negro*.

```{r}
library(wordVectors)
library(ggplot2)
```


## Null identity models

```{r warning = FALSE, message=FALSE}
dir <- "../Ebony_ID/"
ll <- list.files(dir, pattern = ".bin")
model_list <- list()
for(m in 1:length(ll)){
  model_list[[m]] = read.vectors(paste0(dir, ll[m]))
}
```

## Association Trend Plotter 

```{r}
trend_plotter <- function(word_set_1, word_set_2, model_list){
  assoc <- c()
  for(m in 1:length(ll)){
  
  assoc <- c(assoc, 
             cosineSimilarity(model_list[[m]][[word_set_1, average = TRUE]], 
                              model_list[[m]][[word_set_2, average = TRUE]]))
  }
  df <- data.frame("year" =  c(1961:1976),
                   "score" = assoc)
  p <- qplot(year, score, data = df, xlab = "year", ylab = "association score") +  
            geom_smooth(method = "lm", size = 1.5) +
            ggtitle("trend plot")
  p
}
```

## Common consistent words

### racial & discrimination 

```{r}
trend_plotter(c("racial"), c("discrimination"), model_list)
```


### econonic & social

```{r}
trend_plotter(c("social"), c("economic"), model_list)
```


### civil rights & movement

```{r}
trend_plotter(c("civil_rights"), c("movement"), model_list)
```

### jazz & music

```{r}
trend_plotter(c("jazz"), c("music"), model_list)
```


### discrimination & segregation

```{r}
trend_plotter(c("discrimination"), c("segregation"), model_list)
```


### race & relations

```{r}
trend_plotter(c("race"), c("relations"), model_list)
```


## Pre 1968 words

### rock & roll

```{r}
trend_plotter(c("rock"), c("roll"), model_list)
```

### uncle & toms

```{r}
trend_plotter(c("uncle"), c("toms"), model_list)
```

### creed & race

```{r}
trend_plotter(c("creed"), c("race"), model_list)
```

### freed & slaves

```{r}
trend_plotter(c("freed"), c("slaves"), model_list)
```

### declaration & independence

```{r}
trend_plotter(c("declaration"), c("independence"), model_list)
```

### constitutional & rights

```{r}
trend_plotter(c("constitutional"), c("rights"), model_list)
```

## post 1968 words

### health & care

```{r}
trend_plotter(c("health"), c("care"), model_list)
```

### health & mental

```{r}
trend_plotter(c("health"), c("mental"), model_list)
```

### drug & addiction

```{r}
trend_plotter(c("drug"), c("addiction"), model_list)
```

### blues & jazz

```{r}
trend_plotter(c("blues"), c("jazz"), model_list)
```

### blues & music

```{r}
trend_plotter(c("blues"), c("music"), model_list)
```

### black & community

```{r}
trend_plotter(c("black"), c("community"), model_list)
```


## Black World/ Negro Digest words

### civil & war

```{r}
trend_plotter(c("civil"), c("war"), model_list)
```


### racism & oppression

```{r}
trend_plotter(c("racism"), c("oppression"), model_list)
```

### struggle & oppression

```{r}
trend_plotter(c("struggle"), c("oppression"), model_list)
```

### against & oppression

```{r}
trend_plotter(c("against"), c("oppression"), model_list)
```

### blues & spiritual

```{r}
trend_plotter(c("blues"), c("spiritual"), model_list)
```

### college & graduate

```{r}
trend_plotter(c("college"), c("graduate"), model_list)
```

### education & schools

```{r}
trend_plotter(c("education"), c("schools"), model_list)
```










