---
title: "CountClust on Ebony articles - no black, negro terms"
author: "Kushal K Dey"
date: "4/11/2018"
output: html_document
---

## Packages

```{r}
library(CountClust)
library(ggplot2)
```

## Intro

We apply CountClust on the word frequencies for yearly data from Ebony 
articles. We remove identity terms - *black*, *negro* and *afroamerican* - and 
see which terms affect the clustering now. Here we present the results for 
the second case study. 

## Load Data

We first read the counts table of word occurrences in Ebony articles every year.

```{r}
tab_ebony <- get(load("../output/Document_Term_Matrix_Ebony.rda"))
all_words_ebony <- get(load("../output/all_words_ebony.rda"))
```

## Processing and Filtering Data

Next we fit the CountClust model to the tabulated counts data. We first remove 
the words that occur in only one or two years of text data. 

```{r}
low_occur_words <- apply(tab_ebony, 2, function(x) return(sum(x[x!=0])))
tab2_ebony <- tab_ebony[, which(low_occur_words > 2)]
```

Also remove the words that have just two characters as they are usually suffix-es or wrongly
interpreted characters.

```{r}
tab3_ebony <- tab2_ebony[, which(nchar(colnames(tab2_ebony)) > 2)]
```

```{r}
negro_words <- grep("negro", colnames(tab3_ebony))
black_words <- match(c("black", "blacks", "blackman"), colnames(tab3_ebony))
afroamerican_words <- match(c("african", "afroamerican"), colnames(tab3_ebony))
tl_words <- which(substring(colnames(tab3_ebony), 1,2) == "tl")
tab4_ebony <- tab3_ebony[, - c(negro_words, black_words, afroamerican_words, tl_words)]
```

## Fit CountClust

```{r echo=TRUE, eval=FALSE}
topic_clus <- list()
for(k in 2:5){
  topic_clus[[k]] <- maptpx::topics(tab4_ebony, K=k, tol = 1)
}
save(topic_clus, file = "../output/Ebony_CountClust_no_black_negro.rda")

```

```{r}
topic_clus <- get(load("../output/Ebony_CountClust_no_black_negro.rda"))
```

## Visualization

### K= 2 

```{r fig.width = 3, fi.height = 5}
omega <- topic_clus[[2]]$omega
annotation <- data.frame(
  sample_id = paste0("X", c(1:NROW(omega))),
  tissue_label = factor(rownames(omega),
                        levels = rownames(omega)))

rownames(omega) <- annotation$sample_id;

StructureGGplot(omega = omega,
                annotation = annotation,
                palette = RColorBrewer::brewer.pal(8, "Accent"),
                yaxis_label = "Years of Publication",
                order_sample = TRUE,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"))

```

### K= 3

```{r fig.width = 3, fi.height = 5}
omega <- topic_clus[[3]]$omega
annotation <- data.frame(
  sample_id = paste0("X", c(1:NROW(omega))),
  tissue_label = factor(rownames(omega),
                        levels = rownames(omega)))

rownames(omega) <- annotation$sample_id;

StructureGGplot(omega = omega,
                annotation = annotation,
                palette = RColorBrewer::brewer.pal(8, "Accent"),
                yaxis_label = "Years of Publication",
                order_sample = TRUE,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"))

```

### K= 4

```{r fig.width = 3, fi.height = 5}
omega <- topic_clus[[4]]$omega
annotation <- data.frame(
  sample_id = paste0("X", c(1:NROW(omega))),
  tissue_label = factor(rownames(omega),
                        levels = rownames(omega)))

rownames(omega) <- annotation$sample_id;

StructureGGplot(omega = omega,
                annotation = annotation,
                palette = RColorBrewer::brewer.pal(8, "Accent"),
                yaxis_label = "Years of Publication",
                order_sample = TRUE,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"))

```

### K= 5

```{r fig.width = 3, fi.height = 5}
omega <- topic_clus[[5]]$omega
annotation <- data.frame(
  sample_id = paste0("X", c(1:NROW(omega))),
  tissue_label = factor(rownames(omega),
                        levels = rownames(omega)))

rownames(omega) <- annotation$sample_id;

StructureGGplot(omega = omega,
                annotation = annotation,
                palette = RColorBrewer::brewer.pal(8, "Accent"),
                yaxis_label = "Years of Publication",
                order_sample = TRUE,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"))

```

## Top driving words in clusters 

### K=2

```{r}
out <- ExtractTopFeatures(topic_clus[[2]]$theta, top_features = 100, method = "poisson", options = "min")
driving_words <- t(apply(out$indices, c(1,2), function(x) return(rownames(topic_clus[[2]]$theta)[x])))
driving_words[1:50,]
```

### K=3

```{r}
out <- ExtractTopFeatures(topic_clus[[3]]$theta, top_features = 100, method = "poisson", options = "min")
driving_words <- t(apply(out$indices, c(1,2), function(x) return(rownames(topic_clus[[2]]$theta)[x])))
driving_words[1:50,]
```

### K=4

```{r}
out <- ExtractTopFeatures(topic_clus[[4]]$theta, top_features = 100, method = "poisson", options = "min")
driving_words <- t(apply(out$indices, c(1,2), function(x) return(rownames(topic_clus[[2]]$theta)[x])))
driving_words[1:50,]
```

### K=5

```{r}
out <- ExtractTopFeatures(topic_clus[[5]]$theta, top_features = 100, method = "poisson", options = "min")
driving_words <- t(apply(out$indices, c(1,2), function(x) return(rownames(topic_clus[[2]]$theta)[x])))
driving_words[1:50,]
```

## SessionInfo

```{r}
sessionInfo()
```

