---
title: "CountClust on Ebony + Black World/Negro Digest"
author: "Kushal K Dey"
date: "4/11/2018"
output: html_document
---

```{r}
library(CountClust)
library(ggplot2)
```


We apply CountClust on the word frequencies for yearly data from Ebony 
articles and Black World/ Negro Digest articles. We exclude terms like 
*black*, *negro* and *afroamerican* as they are known to be drivers of 
clusters.

We first read the counts table of word occurrences in Ebony 
and Black World/Negro Digest articles for every year.

```{r}
tab_ebony <- get(load("../output/table_word_frequencies_ebony.rda"))
all_words_ebony <- get(load("../output/all_words_ebony.rda"))

tab_bl_nd <- get(load("../output/table_word_frequencies_BL_ND.rda"))
all_words_bl_nd <- get(load("../output/all_words_BL_ND.rda"))
```

Combining the data.

```{r}
common_words <- intersect(all_words_ebony, all_words_bl_nd)
tab_pooled <- rbind(tab_ebony[,match(common_words, all_words_ebony)],
                    tab_bl_nd[,match(common_words, all_words_bl_nd)])

rownames(tab_pooled) <- c(paste0("Ebony_", 1961:1976), 
                          paste0("ND_", 1961:1970), paste0("BL_", 1970:1976))

```

Filter out words

```{r}
low_occur_words <- apply(tab_pooled, 2, function(x) return(sum(x[x!=0])))
tab2_pooled <- tab_pooled[, which(low_occur_words > 2)]
```

```{r}
tab3_pooled <- tab2_pooled[, which(nchar(colnames(tab2_pooled)) > 2)]

negro_words <- grep("negro", colnames(tab3_pooled))
black_words <- match(c("black", "blacks", "blackman"), colnames(tab3_pooled))
afroamerican_words <- match(c("african", "afroamerican"), colnames(tab3_pooled))
tl_words <- which(substring(colnames(tab3_pooled), 1,2) == "tl")

tab4_pooled <- tab3_pooled[, - c(negro_words, black_words, afroamerican_words, tl_words)]
```

## Fitting CountClust

```{r echo=TRUE, eval=FALSE}
topic_clus <- list()
for(k in 2:4){
  topic_clus[[k]] <- maptpx::topics(tab4_pooled, K=k, tol = 1)
}
save(topic_clus, file = "../output/BL_ND_Ebony_CountClust_no_black_negro.rda")

```

```{r}
topic_clus <- get(load("../output/BL_ND_Ebony_CountClust_no_black_negro.rda"))
```

## K = 2

### STRUCTURE plot 

```{r fig.width = 3, fi.height = 5}
omega <- topic_clus[[2]]$omega
annotation <- data.frame(
  sample_id = paste0("X", c(1:NROW(omega))),
  tissue_label = factor(rownames(omega),
                        levels = rownames(omega)))

rownames(omega) <- annotation$sample_id;

StructureGGplot(omega = omega,
                annotation = annotation,
                palette = RColorBrewer::brewer.pal(8, "Accent"),
                yaxis_label = "Years of Publication",
                order_sample = TRUE,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"))

```

### Top driving words 

```{r}
out <- ExtractTopFeatures(topic_clus[[2]]$theta, top_features = 50, method = "poisson", options = "min")
driving_words <- t(apply(out$indices, c(1,2), function(x) return(rownames(topic_clus[[2]]$theta)[x])))
driving_words[1:20,]
```

## K = 3

### STRUCTURE plot 

```{r fig.width = 3, fi.height = 5}
omega <- topic_clus[[3]]$omega
annotation <- data.frame(
  sample_id = paste0("X", c(1:NROW(omega))),
  tissue_label = factor(rownames(omega),
                        levels = rownames(omega)))

rownames(omega) <- annotation$sample_id;

StructureGGplot(omega = omega,
                annotation = annotation,
                palette = RColorBrewer::brewer.pal(8, "Accent"),
                yaxis_label = "Years of Publication",
                order_sample = TRUE,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"))

```

### Top driving words 

```{r}
out <- ExtractTopFeatures(topic_clus[[3]]$theta, top_features = 50, method = "poisson", options = "min")
driving_words <- t(apply(out$indices, c(1,2), function(x) return(rownames(topic_clus[[3]]$theta)[x])))
driving_words[1:20,]
```

## K = 4

### STRUCTURE plot 

```{r fig.width = 3, fi.height = 5}
omega <- topic_clus[[4]]$omega
annotation <- data.frame(
  sample_id = paste0("X", c(1:NROW(omega))),
  tissue_label = factor(rownames(omega),
                        levels = rownames(omega)))

rownames(omega) <- annotation$sample_id;

StructureGGplot(omega = omega,
                annotation = annotation,
                palette = RColorBrewer::brewer.pal(8, "Accent"),
                yaxis_label = "Years of Publication",
                order_sample = TRUE,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"))

```

### Top driving words 

```{r}
out <- ExtractTopFeatures(topic_clus[[4]]$theta, top_features = 50, method = "poisson", options = "min")
driving_words <- t(apply(out$indices, c(1,2), function(x) return(rownames(topic_clus[[4]]$theta)[x])))
driving_words[1:20,]
```

