---
title: "CountClust on Black World Negro Digest - no black, negro terms"
author: "Kushal K Dey"
date: "4/11/2018"
output: html_document
---

```{r}
library(CountClust)
library(ggplot2)
```


## Introduction

We apply CountClust on the word frequencies for yearly data from Negro Digest,
Black World articles. In one case - we include terms like *black*, *negro* and
*afroamerican* terms, the usage of which are known to have changed over the years. 
In other case, we remove these terms and see which terms affect the clustering
now. Here we present the results for the second case study.

```{r}
tab_bl_nd <- get(load("../output/table_word_frequencies_BL_ND.rda"))
all_words_bl_nd <- get(load("../output/all_words_BL_ND.rda"))
```

## Filtering words 

Next we fit the CountClust model to the tabulated counts data. We first remove 
the words that occur in only one or two years of text data. 

```{r}
low_occur_words <- apply(tab_bl_nd, 2, function(x) return(sum(x[x!=0])))
tab2_bl_nd <- tab_bl_nd[, which(low_occur_words > 2)]
```

Also remove the words that have just two characters as they are usually suffix-es or wrongly
interpreted characters.

```{r}
tab3_bl_nd <- tab2_bl_nd[, which(nchar(colnames(tab2_bl_nd)) > 2)]

negro_words <- grep("negro", colnames(tab3_bl_nd))
black_words <- match(c("black", "blacks", "blackman"), colnames(tab3_bl_nd))
afroamerican_words <- match(c("african", "afroamerican"), colnames(tab3_bl_nd))

tab4_bl_nd <- tab3_bl_nd[, - c(negro_words, black_words, afroamerican_words)]
```


## Fitting CountClust

```{r echo=TRUE, eval=FALSE}
topic_clus <- list()
for(k in 2:4){
  topic_clus[[k]] <- maptpx::topics(tab4_bl_nd, K=k, tol = 1)
}
save(topic_clus, file = "../output/BL_ND_CountClust_no_black_negro.rda")

```

```{r}
topic_clus <- get(load("../output/BL_ND_CountClust_no_black_negro.rda"))
```

## K = 2

### STRUCTURE plot 

```{r fig.width = 3, fi.height = 5}
omega <- topic_clus[[2]]$omega
annotation <- data.frame(
  sample_id = paste0("X", c(1:NROW(omega))),
  tissue_label = factor(rownames(omega),
                        levels = rownames(omega)))

rownames(omega) <- annotation$sample_id;

StructureGGplot(omega = omega,
                annotation = annotation,
                palette = RColorBrewer::brewer.pal(8, "Accent"),
                yaxis_label = "Years of Publication",
                order_sample = TRUE,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"))

```

### Top driving words 

```{r}
out <- ExtractTopFeatures(topic_clus[[2]]$theta, top_features = 50, method = "poisson", options = "min")
driving_words <- t(apply(out$indices, c(1,2), function(x) return(rownames(topic_clus[[2]]$theta)[x])))
driving_words[1:20,]
```

## K = 3

### STRUCTURE plot 

```{r fig.width = 3, fi.height = 5}
omega <- topic_clus[[3]]$omega
annotation <- data.frame(
  sample_id = paste0("X", c(1:NROW(omega))),
  tissue_label = factor(rownames(omega),
                        levels = rownames(omega)))

rownames(omega) <- annotation$sample_id;

StructureGGplot(omega = omega,
                annotation = annotation,
                palette = RColorBrewer::brewer.pal(8, "Accent"),
                yaxis_label = "Years of Publication",
                order_sample = TRUE,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"))

```

### Top driving words 

```{r}
out <- ExtractTopFeatures(topic_clus[[3]]$theta, top_features = 50, method = "poisson", options = "min")
driving_words <- t(apply(out$indices, c(1,2), function(x) return(rownames(topic_clus[[3]]$theta)[x])))
driving_words[1:20,]
```

## K = 4

### STRUCTURE plot 

```{r fig.width = 3, fi.height = 5}
omega <- topic_clus[[4]]$omega
annotation <- data.frame(
  sample_id = paste0("X", c(1:NROW(omega))),
  tissue_label = factor(rownames(omega),
                        levels = rownames(omega)))

rownames(omega) <- annotation$sample_id;

StructureGGplot(omega = omega,
                annotation = annotation,
                palette = RColorBrewer::brewer.pal(8, "Accent"),
                yaxis_label = "Years of Publication",
                order_sample = TRUE,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"))

```

### Top driving words 

```{r}
out <- ExtractTopFeatures(topic_clus[[4]]$theta, top_features = 50, method = "poisson", options = "min")
driving_words <- t(apply(out$indices, c(1,2), function(x) return(rownames(topic_clus[[4]]$theta)[x])))
driving_words[1:20,]
```
