---
title: "CountClust on Ebony articles"
author: "Kushal K Dey"
date: "4/11/2018"
output: html_document
---

```{r}
library(CountClust)
library(ggplot2)
```

## Introduction

We apply CountClust on the word frequencies for yearly data from Ebony articles. 
In one case - we include terms like *black* and *negro*, the usage of which are
known to have changed over the years. In other case, we remove these terms and
see which terms affect the clustering now. Here we present the results for the 
first case study. 

We first read the counts table of word occurrences in Ebony articles every year.

```{r}
tab_ebony <- get(load("../output/table_word_frequencies_ebony.rda"))
all_words_ebony <- get(load("../output/all_words_ebony.rda"))
```

## Filtering words 

Next we fit the CountClust model to the tabulated counts data. We first remove 
the words that occur in only one or two years of text data. 

```{r}
low_occur_words <- apply(tab_ebony, 2, function(x) return(sum(x[x!=0])))
tab2_ebony <- tab_ebony[, which(low_occur_words > 2)]
```

Also remove the words that have just two characters as they are usually suffix-es or wrongly
interpreted characters.

```{r}
tab3_ebony <- tab2_ebony[, which(nchar(colnames(tab2_ebony)) > 2)]

tl_words <- which(substring(colnames(tab3_ebony), 1,2) == "tl")
tab4_ebony <- tab3_ebony[, -tl_words]
```

## Fitting CountClust

```{r echo=TRUE, eval=FALSE}
topic_clus <- list()
for(k in 2:4){
  topic_clus[[k]] <- maptpx::topics(tab4_ebony, K=k, tol = 1)
}
save(topic_clus, file = "../output/Ebony_CountClust.rda")

```

```{r}
topic_clus <- get(load("../output/Ebony_CountClust.rda"))
```

## K = 2

### STRUCTURE plot 

```{r fig.width = 3, fi.height = 5}
omega <- topic_clus[[2]]$omega
annotation <- data.frame(
  sample_id = paste0("X", c(1:NROW(omega))),
  tissue_label = factor(rownames(omega),
                        levels = rownames(omega)))

rownames(omega) <- annotation$sample_id;

StructureGGplot(omega = omega,
                annotation = annotation,
                palette = RColorBrewer::brewer.pal(8, "Accent"),
                yaxis_label = "Years of Publication",
                order_sample = TRUE,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"))

```

### Top driving words 

```{r}
out <- ExtractTopFeatures(topic_clus[[2]]$theta, top_features = 50, method = "poisson", options = "min")
driving_words <- t(apply(out$indices, c(1,2), function(x) return(rownames(topic_clus[[2]]$theta)[x])))
driving_words[1:20,]
```

## K = 3

### STRUCTURE plot 

```{r fig.width = 3, fi.height = 5}
omega <- topic_clus[[3]]$omega
annotation <- data.frame(
  sample_id = paste0("X", c(1:NROW(omega))),
  tissue_label = factor(rownames(omega),
                        levels = rownames(omega)))

rownames(omega) <- annotation$sample_id;

StructureGGplot(omega = omega,
                annotation = annotation,
                palette = RColorBrewer::brewer.pal(8, "Accent"),
                yaxis_label = "Years of Publication",
                order_sample = TRUE,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"))

```

### Top driving words 

```{r}
out <- ExtractTopFeatures(topic_clus[[3]]$theta, top_features = 50, method = "poisson", options = "min")
driving_words <- t(apply(out$indices, c(1,2), function(x) return(rownames(topic_clus[[3]]$theta)[x])))
driving_words[1:20,]
```

## K = 4

### STRUCTURE plot 

```{r fig.width = 3, fi.height = 5}
omega <- topic_clus[[4]]$omega
annotation <- data.frame(
  sample_id = paste0("X", c(1:NROW(omega))),
  tissue_label = factor(rownames(omega),
                        levels = rownames(omega)))

rownames(omega) <- annotation$sample_id;

StructureGGplot(omega = omega,
                annotation = annotation,
                palette = RColorBrewer::brewer.pal(8, "Accent"),
                yaxis_label = "Years of Publication",
                order_sample = TRUE,
                axis_tick = list(axis_ticks_length = .1,
                                 axis_ticks_lwd_y = .1,
                                 axis_ticks_lwd_x = .1,
                                 axis_label_size = 7,
                                 axis_label_face = "bold"))

```

### Top driving words 

```{r}
out <- ExtractTopFeatures(topic_clus[[4]]$theta, top_features = 50, method = "poisson", options = "min")
driving_words <- t(apply(out$indices, c(1,2), function(x) return(rownames(topic_clus[[4]]$theta)[x])))
driving_words[1:20,]
```



