---
title: "Trends in top distinguishing words in CountClust"
author: "Kushal K Dey"
date: "7/29/2018"
output: html_document
---

## Intro

In this chapter, we plot the trends in top distinguishing words from fitting
topic models on the yearly issues of the Negro Digest/ Black World and the 
Ebony magazines.

## Black World/Nwgro Digest 

### Word frequencies

```{r}
BL_ND_data <- get(load( "../output/Document_Term_Matrix_BW_ND.rda"))
BL_ND_data_norm <- t(apply(BL_ND_data, 1, function(x) return(x/sum(x))))
```

### theater

```{r fig.height=4, fig.width=4}
plot(BL_ND_data_norm[, "theater"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "theater")
axis(1, at=1:dim(BL_ND_data_norm)[1], 
     rownames(BL_ND_data_norm), las = 2, cex.axis = 0.7)
```

### broadside

```{r fig.height=4, fig.width=4}
plot(BL_ND_data_norm[, "broadside"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "broadside")
axis(1, at=1:dim(BL_ND_data_norm)[1], 
     rownames(BL_ND_data_norm), las = 2, cex.axis = 0.7)
```

### aesthetics

```{r fig.height=4, fig.width=4}
plot(BL_ND_data_norm[, "aesthetics"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "aesthetics")
axis(1, at=1:dim(BL_ND_data_norm)[1], 
     rownames(BL_ND_data_norm), las = 2, cex.axis = 0.7)
```

### literature

```{r fig.height=4, fig.width=4}
plot(BL_ND_data_norm[, "literature"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "literature")
axis(1, at=1:dim(BL_ND_data_norm)[1], 
     rownames(BL_ND_data_norm), las = 2, cex.axis = 0.7)
```

### civil rights

```{r fig.height=4, fig.width=4}
plot(BL_ND_data_norm[, "civil_rights"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "civil rights")
axis(1, at=1:dim(BL_ND_data_norm)[1], 
     rownames(BL_ND_data_norm), las = 2, cex.axis = 0.7)
```

### righters

```{r fig.height=4, fig.width=4}
plot(BL_ND_data_norm[, "righters"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "righters")
axis(1, at=1:dim(BL_ND_data_norm)[1], 
     rownames(BL_ND_data_norm), las = 2, cex.axis = 0.7)
```

### segregation

```{r fig.height=4, fig.width=4}
plot(BL_ND_data_norm[, "segregation"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "segregation")
axis(1, at=1:dim(BL_ND_data_norm)[1], 
     rownames(BL_ND_data_norm), las = 2, cex.axis = 0.7)
```

### race

```{r fig.height=4, fig.width=4}
plot(BL_ND_data_norm[, "race"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "race")
axis(1, at=1:dim(BL_ND_data_norm)[1], 
     rownames(BL_ND_data_norm), las = 2, cex.axis = 0.7)
```

### black panther

```{r fig.height=4, fig.width=4}
plot(BL_ND_data_norm[, "black_panther"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "black panther")
axis(1, at=1:dim(BL_ND_data_norm)[1], 
     rownames(BL_ND_data_norm), las = 2, cex.axis = 0.7)
```

## Ebony

### Word frequencies

```{r}
ebony_data <- get(load( "../output/Document_Term_Matrix_Ebony.rda"))
ebony_data_norm <- t(apply(ebony_data, 1, function(x) return(x/sum(x))))
```

### theater

```{r fig.height=4, fig.width=4}
plot(ebony_data_norm[, "literature"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "literature")
axis(1, at=1:dim(ebony_data_norm)[1], 
     rownames(ebony_data_norm), las = 2, cex.axis = 0.7)
```

### drama

```{r fig.height=4, fig.width=4}
plot(ebony_data_norm[, "drama"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "drama")
axis(1, at=1:dim(ebony_data_norm)[1], 
     rownames(ebony_data_norm), las = 2, cex.axis = 0.7)
```

### black panther

```{r fig.height=4, fig.width=4}
plot(ebony_data_norm[, "black_panther"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "black panther")
axis(1, at=1:dim(ebony_data_norm)[1], 
     rownames(ebony_data_norm), las = 2, cex.axis = 0.7)
```

### watergate

```{r fig.height=4, fig.width=4}
plot(ebony_data_norm[, "watergate"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "watergate")
axis(1, at=1:dim(ebony_data_norm)[1], 
     rownames(ebony_data_norm), las = 2, cex.axis = 0.7)
```

### civil rights

```{r fig.height=4, fig.width=4}
plot(ebony_data_norm[, "civil_rights"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "civil rights")
axis(1, at=1:dim(ebony_data_norm)[1], 
     rownames(ebony_data_norm), las = 2, cex.axis = 0.7)
```

### segregation

```{r fig.height=4, fig.width=4}
plot(ebony_data_norm[, "segregation"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "segregation")
axis(1, at=1:dim(ebony_data_norm)[1], 
     rownames(ebony_data_norm), las = 2, cex.axis = 0.7)
```

### race

```{r fig.height=4, fig.width=4}
plot(ebony_data_norm[, "race"], 
     col = "red", pch = 20, cex = 1.5, xaxt = "n", 
     ylab = "occurrence prop.", xlab = "", main = "race")
axis(1, at=1:dim(ebony_data_norm)[1], 
     rownames(ebony_data_norm), las = 2, cex.axis = 0.7)
```
