---
title: "Null identity analysis of top trending words close to (black, negro) for Ebony"
author: "Kushal K Dey"
date: "4/12/2018"
output: html_document
---

## Introduction

In this script, we look at the top trending words related to black and negro 
for Ebony magazine and then see what happens to the trend when the black and 
negro words are combined together. Do we see an identity bias?

```{r}
library(wordVectors)
library(ggplot2)
```

## Load word2vec models

We load the word2vec model fits.

### Null identity models

```{r warning = FALSE, message=FALSE}
dir <- "../Ebony_ID/"
ll <- list.files(dir, pattern = ".bin")
model_list_1 <- list()
for(m in 1:length(ll)){
  model_list_1[[m]] = read.vectors(paste0(dir, ll[m]))
}
```

### Full model

```{r warning = FALSE, message=FALSE}
dirs <- c("../Ebony/1961/", "../Ebony/1962/", "../Ebony/1963/",
          "../Ebony/1964/", "../Ebony/1965/", "../Ebony/1966/",
          "../Ebony/1967/", "../Ebony/1968/", "../Ebony/1969/",
          "../Ebony/1970/", "../Ebony/1971/", "../Ebony/1972/",
          "../Ebony/1973/", "../Ebony/1974/", "../Ebony/1975/",
          "../Ebony/1976/")

model_list_2 <- list()
for(m in 1:length(dirs)){
  model_list_2[[m]] = read.vectors(paste0(dirs[m], "pooled_word2vec.bin"))
}
```


## Association Trend Plotter 

```{r}
trend_plotter <- function(word_set_1, word_set_2, model_list){
  assoc <- c()
  for(m in 1:length(ll)){
  
  assoc <- c(assoc, 
             cosineSimilarity(model_list[[m]][[word_set_1, average = TRUE]], 
                              model_list[[m]][[word_set_2, average = TRUE]]))
  }
  df <- data.frame("year" =  c(1961:1976),
                   "score" = assoc)
  p <- qplot(year, score, data = df, xlab = "year", ylab = "association score") +  
            geom_smooth(method = "lm", size = 1.5) +
            ggtitle("trend plot")
  p
}
```

## [Black, Negro] vs civil rights 

```{r}
trend_plotter(c("black", "blacks"), c("civil_rights"), model_list_1)
```

## [Black] vs civil rights

```{r}
trend_plotter(c("black", "blacks"), c("civil_rights"), model_list_2)
```

## [negro] vs civil rights

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("civil_rights"), model_list_2)
```


## [Black, Negro] vs economy

```{r}
trend_plotter(c("black", "blacks"), c("economy"), model_list_1)
```

## Black vs economy

```{r}
trend_plotter(c("black", "blacks"), c("economy"), model_list_2)
```

## Negro vs economy 

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("economy"), model_list_2)
```



## [Black, Negro] vs opportunities

```{r}
trend_plotter(c("black", "blacks"), c("opportunities"), model_list_1)
```

## Black vs opportunities 

```{r}
trend_plotter(c("black", "blacks"), c("opportunities"), model_list_2)
```

## Negro vs opportunities 

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("opportunities"), model_list_2)
```

## [Black, Negro] vs qualified

```{r}
trend_plotter(c("black", "blacks"), c("qualified"), model_list_1)
```

## [Black] vs qualified

```{r}
trend_plotter(c("black", "blacks"), c("qualified"), model_list_2)
```

## [Negro] vs qualified

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("qualified"), model_list_2)
```

## [Black, Negro] vs progress

```{r}
trend_plotter(c("black", "blacks"), c("progress"), model_list_1)
```

## [Black, Negro] vs progress

```{r}
trend_plotter(c("black", "blacks"), c("progress"), model_list_2)
```


## [Negro] vs progress

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("progress"), model_list_2)
```

## [Black, Negro] vs leaders

```{r}
trend_plotter(c("black", "blacks"), c("leaders", "ministers"), model_list_1)
```

## [Black, Negro] vs leaders

```{r}
trend_plotter(c("black", "blacks"), c("leaders", "ministers"), model_list_2)
```

## [Black, Negro] vs leaders

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("leaders", "ministers"), model_list_2)
```

## [Black, Negro] vs white

```{r}
trend_plotter(c("black", "blacks"), c("white"), model_list_1)
```

## [Black] vs white

```{r}
trend_plotter(c("black", "blacks"), c("white"), model_list_2)
```

## [Negro] vs white

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("white"), model_list_2)
```

## [Black, Negro] vs studies

```{r}
trend_plotter(c("black", "blacks"), c("studies"), model_list_1)
```


## [Black] vs studies

```{r}
trend_plotter(c("black", "blacks"), c("studies"), model_list_2)
```

## [Negro] vs studies

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("studies"), model_list_2)
```

## [Black, Negro] vs bright

```{r}
trend_plotter(c("black", "blacks"), c("bright"), model_list_1)
```

## [Black] vs bright

```{r}
trend_plotter(c("black", "blacks"), c("bright"), model_list_2)
```


## [Negro] vs bright

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("bright"), model_list_2)
```


## [Black, Negro] vs rights

```{r}
trend_plotter(c("black", "blacks"), c("rights"), model_list_1)
```


## [Black] vs rights

```{r}
trend_plotter(c("black", "blacks"), c("rights"), model_list_2)
```

## [Negro]  vs rights

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("rights"), model_list_2)
```


## [Black, Negro] vs employment, jobs

```{r}
trend_plotter(c("black", "blacks"), c("employment", "jobs", "income", "unemployment"), model_list_1)
```

## [Black] vs employment, jobs

```{r}
trend_plotter(c("black", "blacks"), c("employment", "jobs", "income", "unemployment"), model_list_2)
```

## [Negro] vs employment, jobs

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("employment", "jobs", "income", "unemployment"), model_list_2)
```


## [Black, Negro] vs education

```{r}
trend_plotter(c("black", "blacks"), c("education"), model_list_1)
```

## [Black] vs education

```{r}
trend_plotter(c("black", "blacks"), c("education"), model_list_2)
```

## [Negro] vs education

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("education"), model_list_2)
```

## [Black, Negro] vs minorities

```{r}
trend_plotter(c("black", "blacks"), c("minorities"), model_list_1)
```

## [Black] vs minorities

```{r}
trend_plotter(c("black", "blacks"), c("minorities"), model_list_2)
```

## [Negro] vs minorities

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("minorities"), model_list_2)
```

## [Black, Negro] vs families

```{r}
trend_plotter(c("black", "blacks"), c("families"), model_list_1)
```

## [Black] vs families

```{r}
trend_plotter(c("black", "blacks"), c("families"), model_list_2)
```

## [Negro] vs families

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("families"), model_list_2)
```

## [Black, Negro] vs deprived

```{r}
trend_plotter(c("black", "blacks"), c("deprived"), model_list_1)
```

## [Black] vs deprived

```{r}
trend_plotter(c("black", "blacks"), c("deprived"), model_list_2)
```

## [Negro] vs deprived

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("deprived"), model_list_2)
```

## [Black, Negro] vs inferior

```{r}
trend_plotter(c("black", "blacks"), c("inferior"), model_list_1)
```


## [Black] vs inferior

```{r}
trend_plotter(c("black", "blacks"), c("inferior"), model_list_2)
```

## [Negro] vs inferior

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("inferior"), model_list_2)
```

## SessionInfo

```{r}
sessionInfo()
```


