---
title: "Trends in words Black and Negro over years"
author: "Kushal K Dey"
date: "7/27/2018"
output: html_document
---

## Intro

In this second chapter of the tutorial, we use the yearly aggregated
text files, `pooled.txt`,  created for each year of publication of the magazines
of interest - Black World/ Negro Digest and Ebony.

The 1960-1970s era saw the word `negro(es)` gradually falling out of favor and the
word `black(s)` becoming a more commonly used identity term.

## Packages

```{r message = FALSE, warning=FALSE}
library(wordVectors)
library(gridExtra)
library(ggplot2)
library(scales)
```

## Black World/ Negro Digest

### All words

```{r echo=TRUE, eval=FALSE}

dirs <- c("../BL_ND/BL_ND_1961/",
          "../BL_ND/BL_ND_1962/",
          "../BL_ND/BL_ND_1963/",
          "../BL_ND/BL_ND_1964/",
          "../BL_ND/BL_ND_1965/",
          "../BL_ND/BL_ND_1966/",
          "../BL_ND/BL_ND_1967/",
          "../BL_ND/BL_ND_1968/",
          "../BL_ND/BL_ND_1969/",
          "../BL_ND/BL_ND_1970/",
          "../BL_ND/BL_ND_1971/",
          "../BL_ND/BL_ND_1972/",
          "../BL_ND/BL_ND_1973/",
          "../BL_ND/BL_ND_1974/",
          "../BL_ND/BL_ND_1975/",
          "../BL_ND/BL_ND_1976/")

all_names <- c()
for(m in 1:length(dirs)){
  sentences<-scan(paste0(dirs[m], "pooled.txt"),"character",sep="\n");
  #Replace full stop and comma
  sentences<-gsub("\\.","",sentences)
  sentences<-gsub("\\,","",sentences)
  #Split sentence
  words<-strsplit(sentences," ")
  #Calculate word frequencies
  words.freq<-table(unlist(words));
  all_names <- union(all_names , names(words.freq))
}
```

### Word frequencies

```{r echo=TRUE, eval=FALSE}
tab <- matrix(0, length(dirs), length(all_names))
colnames(tab) <- all_names
rownames(tab) <- c(paste0("ND/BW_", 1961:1976))

for(m in 1:length(dirs)){
  sentences<-scan(paste0(dirs[m], "pooled.txt"),"character",sep="\n");
  #Replace full stop and comma
  sentences<-gsub("\\.","",sentences)
  sentences<-gsub("\\,","",sentences)
  #Split sentence
  words<-strsplit(sentences," ")
  #Calculate word frequencies
  words.freq<-table(unlist(words));
  tab[m, match(names(words.freq), colnames(tab))] <- as.numeric(words.freq)
}

tab[1:5, 1:5]
```

Save the output

```{r echo=TRUE, eval=FALSE}
save(tab, file = "../output/Document_Term_Matrix_BW_ND.rda")
save(all_names, file = "../output/all_words_BW_ND.rda")
```

### Plot trends of black(s) and negro(s)

Load the document term matrix and plot the trends of the words `negro` and `blacks`

```{r}
bl_nd_data <- get(load( "../output/Document_Term_Matrix_BW_ND.rda"))
bl_nd_data_norm <- t(apply(bl_nd_data, 1, function(x) return(x/sum(x))))
black_counts_norm <- apply(bl_nd_data_norm[, c("black", "blacks")], 1, mean)
negro_counts_norm <- apply(bl_nd_data_norm[, c("negro", "negros", "negroes")], 1, mean)
afroamerican_counts_norm <- apply(bl_nd_data_norm[, c("afroamerican", "africanamerican")], 1, mean)
```

```{r}
charts.data <- data.frame("word" = c(rep("black(s)", 16), 
                                     rep("negro(s)", 16)),
                          "year" = factor(c(1961:1976, 
                                          1961:1976),
                                          levels = 1961:1976),
                          "prop" = c(black_counts_norm, 
                                     negro_counts_norm))


p1 <- ggplot() + geom_line(aes(y = prop, x = year, colour = word, group=word),
                           data = charts.data, stat="identity") +
        theme(axis.text.x=element_text(angle=90, hjust=1)) + xlab("year of publication") + 
        ylab("relative occurrence") + ggtitle("Black World/Negro Digest") +
        theme(plot.title = element_text(hjust = 0.5))

p1

```



## Ebony

### All words

```{r echo=TRUE, eval=FALSE}

dirs <- c("../Ebony/1961/", 
          "../Ebony/1962/",
          "../Ebony/1963/",
          "../Ebony/1964/",
          "../Ebony/1965/", 
          "../Ebony/1966/",
          "../Ebony/1967/", 
          "../Ebony/1968/",
          "../Ebony/1969/",
          "../Ebony/1970/", 
          "../Ebony/1971/", 
          "../Ebony/1972/",
          "../Ebony/1973/",
          "../Ebony/1974/", 
          "../Ebony/1975/",
          "../Ebony/1976/")

all_names <- c()
for(m in 1:length(dirs)){
  sentences<-scan(paste0(dirs[m], "pooled.txt"),"character",sep="\n");
  #Replace full stop and comma
  sentences<-gsub("\\.","",sentences)
  sentences<-gsub("\\,","",sentences)
  #Split sentence
  words<-strsplit(sentences," ")
  #Calculate word frequencies
  words.freq<-table(unlist(words));
  all_names <- union(all_names , names(words.freq))
}
```

### Word frequencies

```{r echo=TRUE, eval=FALSE}
tab <- matrix(0, length(dirs), length(all_names))
colnames(tab) <- all_names
rownames(tab) <- c(paste0("Ebony_", 1961:1976))

for(m in 1:length(dirs)){
  sentences<-scan(paste0(dirs[m], "pooled.txt"),"character",sep="\n");
  #Replace full stop and comma
  sentences<-gsub("\\.","",sentences)
  sentences<-gsub("\\,","",sentences)
  #Split sentence
  words<-strsplit(sentences," ")
  #Calculate word frequencies
  words.freq<-table(unlist(words));
  tab[m, match(names(words.freq), colnames(tab))] <- as.numeric(words.freq)
}

tab[1:5, 1:5]
```

Save the output

```{r echo=TRUE, eval=FALSE}
save(tab, file = "../output/Document_Term_Matrix_Ebony.rda")
save(all_names, file = "../output/all_words_Ebony.rda")
```

### Plot trends of black(s) and negro(s)

Load the document term matrix and plot the trends of the words `negro` and `blacks`

```{r}
bl_nd_data <- get(load( "../output/Document_Term_Matrix_Ebony.rda"))
bl_nd_data_norm <- t(apply(bl_nd_data, 1, function(x) return(x/sum(x))))
black_counts_norm <- apply(bl_nd_data_norm[, c("black", "blacks")], 1, mean)
negro_counts_norm <- apply(bl_nd_data_norm[, c("negro", "negros", "negroes")], 1, mean)
afroamerican_counts_norm <- apply(bl_nd_data_norm[, c("afroamerican", "africanamerican")], 1, mean)
```

```{r}
charts.data <- data.frame("word" = c(rep("black(s)", 16), 
                                     rep("negro(s)", 16)),
                          "year" = factor(c(1961:1976, 
                                          1961:1976),
                                          levels = 1961:1976),
                          "prop" = c(black_counts_norm, 
                                     negro_counts_norm))


p2 <- ggplot() + geom_line(aes(y = prop, x = year, colour = word, group=word),
                           data = charts.data, stat="identity") +
        theme(axis.text.x=element_text(angle=90, hjust=1)) + xlab("year of publication") + 
        ylab("relative occurrence") + ggtitle("Ebony") +
        theme(plot.title = element_text(hjust = 0.5))

p2

```

## Multiple plots

```{r fig.width = 10, fig.height = 4}
grid.arrange(p1,p2, nrow = 1, ncol = 2, as.table = FALSE) 
```

## SessionInfo

```{r}
sessionInfo()
```

