---
title: 'word2vec association analysis : Black World/ Negro Digest'
author: "Kushal K Dey"
date: "4/11/2018"
output: html_document
---

## Introduction

In this script, we investigate the association between words or word sets of
interest for the Black World/ Negro Digest magazines. We also track the 
associations across time.

```{r}
library(wordVectors)
library(ggplot2)
```

## Load word2vec models

We load the word2vec model fits.

```{r warning = FALSE, message=FALSE}
dirs <- c("../Negro_Digest/ND_1961/",
          "../Negro_Digest/ND_1962/",
          "../Negro_Digest/ND_1963/",
          "../Negro_Digest/ND_1964/",
          "../Negro_Digest/ND_1965/",
          "../Negro_Digest/ND_1966/",
          "../Negro_Digest/ND_1967/",
          "../Negro_Digest/ND_1968/",
          "../Negro_Digest/ND_1969/",
          "../Negro_Digest/ND_1970/",
          "../Black_World/BL_1970/",
          "../Black_World/BL_1971/",
          "../Black_World/BL_1972/",
          "../Black_World/BL_1973/",
          "../Black_World/BL_1974/",
          "../Black_World/BL_1975/",
          "../Black_World/BL_1976/")


model_list <- list()
for(m in 1:length(dirs)){
  model_list[[m]] = read.vectors(paste0(dirs[m], "pooled_word2vec.bin"))
}
```

## Association Trend Plotter 

```{r}
trend_plotter <- function(word_set_1, word_set_2){
  assoc <- c()
  for(m in 1:length(dirs)){
  
  assoc <- c(assoc, 
             cosineSimilarity(model_list[[m]][[word_set_1, average = TRUE]], 
                              model_list[[m]][[word_set_2, average = TRUE]]))
  }
  df <- data.frame("year" =  c(1961:1970, 1970:1976),
                   "score" = assoc)
  p <- qplot(year, score, data = df, xlab = "year", ylab = "association score") +  
            geom_smooth(method = "lm", size = 1.5) +
            ggtitle("trend plot")
  p
}
```

##  Negro vs Struggle 

```{r}
trend_plotter(c("negro", "negroes", "negro"), c("struggle", "struggles"))
```

##  Black vs Struggle 

```{r}
trend_plotter(c("black", "blacks"), c("struggle", "struggles"))
```


##  [Negro, black] vs Struggle 

```{r}
trend_plotter(c("negro", "negroes", "negro", "black", "blacks"), c("struggle", "struggles"))
```


## Negro vs Revolution 

```{r}
trend_plotter(c("negro", "negroes", "negro"), c("revolution", "movement"))
```

## Negro vs Black

```{r}
trend_plotter(c("negro", "negroes", "negro"), c("black", "blacks"))
```

## Negro vs arts

```{r}
arts <- c("arts", "art", "music", "musicians", "musician",
   "poem", "poems", "poet", "poets",
   "poetry", "literature", "novels",
   "fiction", "theatre", "theater",
   "blues", "jazz", "magazines",
   "magazine", "painting", "sculpture", "painter", "artist", "artists",
   "sculpture", "composer", "prose", "ballads", "anthology" )
trend_plotter(c("negro", "negroes", "negro"), arts)
```

## Black vs arts

```{r}
arts <- c("arts", "art", "music", "musicians", "musician",
   "poem", "poems", "poet", "poets",
   "poetry", "literature", "novels",
   "fiction", "theatre", "theater",
   "blues", "jazz", "magazines",
   "magazine", "painting", "sculpture", "painter", "artist", "artists",
   "sculpture", "composer", "prose", "ballads", "anthology" )
trend_plotter(c("black", "blacks"), arts)
```

## [Black, Negro] vs arts

```{r}
trend_plotter(c("black", "blacks", "negro", "negros", "negroes"), arts)
```

## [Black, Negro] vs slave

```{r}
trend_plotter(c("black", "blacks", "negro", "negros", "negroes"), c("slave", "slaves"))
```

## [Negro] vs slave

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("slave", "slaves"))
```

## [black] vs slave

```{r}
trend_plotter(c("black", "blacks"), c("slave", "slaves"))
```

## Black_panther vs black_power

```{r}
trend_plotter("black_panther", "black_power")
```

## Black vs blues

```{r}
trend_plotter(c("black", "blacks"), "blues")
```

## Black vs blues, jazz

```{r}
trend_plotter(c("black", "blacks"), c("blues", "jazz"))
```

## Negro vs blues, jazz

```{r}
trend_plotter(c("negro", "negros", "negroes"), c("blues", "jazz"))
```

## [Black, Negro] vs blues, jazz

```{r}
trend_plotter(c("negro", "negros", "negroes", "blacks", "black"), c("blues", "jazz"))
```

## afroamerican vs arts

```{r}
trend_plotter(c("afroamerican"), arts)
```

## MLK vs assassination

```{r}
set1 <- c("martin_luther_king", "martin_luther_kings", "dr_king", "dr_kings")
set2 <- c("assassination", "death", "died", "murder", "assassinated", "murdered")
trend_plotter(set1, set2)
```

## Black power vs Stokely

```{r}
trend_plotter(c("stokely", "carmichael"), c("black_power"))
```

## MLK vs civil rights

```{r}
set1 <- c("martin_luther_king", "martin_luther_kings", "dr_king", "dr_kings")
set2 <- c("civil_rights", "rights", "righters")
trend_plotter(set1, set2)
```




