---
title: "Identity null Black World/ Negro Digest word2vec associations"
author: "Kushal K Dey"
date: "4/12/2018"
output: html_document
---

## Introduction

In this script, we investigate the association between words or word sets of
interest for the Black World/ Negro Digest magazine when the identity difference between
black and negro terms has been nullified. We also track the associations across time.

```{r}
library(wordVectors)
library(ggplot2)
```

## Load word2vec models

We load the word2vec model fits.

```{r warning = FALSE, message=FALSE}
dir <- "../BL_ND_ID/"
ll <- list.files(dir, pattern = ".bin")
model_list <- list()
for(m in 1:length(ll)){
  model_list[[m]] = read.vectors(paste0(dir, ll[m]))
}
```

## Association Trend Plotter 

```{r}
trend_plotter <- function(word_set_1, word_set_2){
  assoc <- c()
  for(m in 1:length(ll)){
  
  assoc <- c(assoc, 
             cosineSimilarity(model_list[[m]][[word_set_1, average = TRUE]], 
                              model_list[[m]][[word_set_2, average = TRUE]]))
  }
  df <- data.frame("year" =  c(1961:1970, 1970:1976),
                   "score" = assoc)
  p <- qplot(year, score, data = df, xlab = "year", ylab = "association score") +  
            geom_smooth(method = "lm", size = 1.5) +
            ggtitle("trend plot")
  p
}
```


##  Black vs Struggle - 1

```{r}
trend_plotter(c("black", "blacks"), c("struggle"))
```


##  Black vs Struggle - 2

```{r}
trend_plotter(c("black", "blacks"), c("struggle", "struggles"))
```

##  Black vs civil rights, MLK

```{r}
trend_plotter(c("black", "blacks"), c("civil_rights", "martin_luther_king"))
```

##  Black vs movement 

```{r}
trend_plotter(c("black", "blacks"), c("movement"))
```

##  Black vs protests 

```{r}
trend_plotter(c("black", "blacks"), c("protests", "protest"))
```

##  Black vs vietnam

```{r}
trend_plotter(c("black", "blacks"), c("vietnam"))
```


##  Black vs civil rights

```{r}
trend_plotter(c("black", "blacks"), "civil_rights")
```


## Black vs Revolution 

```{r}
trend_plotter(c("black", "blacks"), c("revolution", "movement"))
```


## Black vs arts

```{r}
arts <- c("arts", "art", "music", "musicians", "musician",
   "poem", "poems", "poet", "poets",
   "poetry", "literature", "novels",
   "fiction", "theatre", "theater",
   "blues", "jazz", "magazines",
   "magazine", "painting", "sculpture", "painter", "artist", "artists",
   "sculpture", "composer", "prose", "ballads", "anthology" )
trend_plotter(c("black", "blacks"), arts)
```

## Black vs slave

```{r}
trend_plotter(c("black", "blacks"), c("slave", "slaves"))
```

## Black vs black_power

```{r}
trend_plotter(c("black", "blacks"), c("black_power"))
```

## Black vs blues

```{r}
trend_plotter(c("black", "blacks"), "blues")
```

## Black vs blues, jazz

```{r}
trend_plotter(c("blacks", "black"), c("blues", "jazz"))
```


